\section{Background and Related Work}
% The idea of natural language based computer interface was born even before the UNIX sytem was released~\cite{sammet1966use,Ballard:1979:PNL:800177.810072}. The central idea was to build compilers 
Early compilers that compile natural language into lower-level instructions~\cite{sammet1966use,Ballard:1979:PNL:800177.810072}
% . However, NLP techniques were preliminary back then, and those systems, relying on manually engineered templates and grammars, had 
failed to handle the rich semantics and ambiguity in natural languages. 
% Besides, some researchers pointed out that making machines to understand our native tongue is a fruitless trial for it lacks mathematical support and programming languages remains simple in the formal system. In short, it was easier for people to learn how to program than for machines to learn natural language. 
While it may be fruitless to mold natural language into a fully functional programming language~\cite{Dijkstra:1978:FNL:647639.760596}, recent work have shown promise on synthesizing high-level code snippets based on their natural language descriptions~\cite{gulwani2010dimensions,DBLP:journals/corr/DesaiGHJKMRR15}.  
% and can be furthur improved through interaction with users~\cite{DBLP:conf/sigmod/GulwaniM14,DBLP:journals/pvldb/LiJ14}.
Initial success on natural language interfaces to database~\cite{Popescu:2003:TTN:604045.604070,DBLP:journals/pvldb/LiJ14} and commercial applications~\cite{DBLP:conf/mobisys/LeGS13,DBLP:conf/acl/QuirkMG15} leveraged data-driven, machine learning based approaches. CmdHelper~\cite{bashsynthesis} applied similar techniques to synthesis shell commands for file system operations trained with StackOverflow\footnote{http://stackoverflow.com/} question-answer pairs. The system has succeed in generating commands up to length 5 that do not contain a ``pipe". Due to high search space complexity and the lack of high-quality training data, many challenges still remain for the system to be practically useful.

% Previous work on shell programming from natural language have shown that the task is extremely difficult~\cite{bashsynthesis,cozzie2011macho,cozzie2012macho,Pedersen-Report}. 


Other shell command synthesis work uses different approaches.
Macho~\cite{cozzie2011macho} is a system that extracts specifications from text in the Linux man-pages\footnote{https://www.kernel.org/doc/man-pages/}, and uses the extracted specifications to guide the generation. However, their approach did not go beyond generating the head commands. The improved version of Macho~\cite{cozzie2012macho} uses command and natural language description pairs instead, combined with a unit test provided by the user, and shows that the combination is effective in pruning the search space. Nevertheless, the results were limited to commands up to length 2.

